### 2016-07-22 results.tex
restructuring

\section{Achieving FP-Security and Privacy}
\heading{FP-security. }  Here we give security proofs and attacks with respect the the FP-security notions just described.
\begin{itemize}
\item \jnote{Would be good to show that RO-based Bloom filter is FP-secure.}
\item FP-security/attacks on bigram/PRF-based double-hashing construction ($h_j(x) = F_{K1}(x) + j\cdot F_{K2}(x) \bmod m$ where the~$x$ are bigrams of names, etc.) \tsnote{Animesh is doing this now}
\item FP-security/attacks on bigram/domain-separated PRF construction ($h_j(x)=F_K(\langle j,x \rangle) \bmod m$, or just assume range of~$F$ is $[m]$.)
\item FP-security/attacks Dong, Chen, Wen ``garbled Bloom filter'' construction
\item ...
\end{itemize}

\heading{Privacy. } Here we give security proofs and attacks with respect the the FP-security notions just described.
\tsnote{Under our current notions, you can never hope to prove privacy bounds that beat the min-entropy of $\distr{U}{n}$.}
\begin{itemize}
\item Prove that the basic BF, in the ROM, is private.  \tsnote{Not at all surprising, but it is the first result one would want in this area.}

>>>>

\section{Achieving Security Notions}
\heading{Correctness. }  Here we give security proofs and attacks with respect to the correctness notions.
\begin{itemize}
\item Show Bloom Filter is correct in the ROM %\jnote{Would be good to show that RO-based Bloom filter is FP-secure.}
\item FP-security/attacks on bigram/PRF-based double-hashing construction ($h_j(x) = F_{K1}(x) + j\cdot F_{K2}(x) \bmod m$ where the~$x$ are bigrams of names, etc.) 
\item FP-security/attacks on bigram/domain-separated PRF construction ($h_j(x)=F_K(\langle j,x \rangle) \bmod m$, or just assume range of~$F$ is $[m]$.)
\item FP-security/attacks Dong, Chen, Wen ``garbled Bloom filter'' construction
\item ...
\end{itemize}

\heading{Privacy. } Here we give security proofs and attacks with respect to the privacy notions we have defined.
\tsnote{Under our current notions, you can never hope to prove privacy bounds that beat the min-entropy of $\distr{U}{n}$.}
\begin{itemize}
\item Prove that the basic BF, in the ROM, is private.  \tsnote{Not at all surprising, but it is the first result one would want in this area.}
